\documentclass[12]{article}

\begin{document}
\title{The Relevance of Mobile Phones And Their Effects To Uganda As A Nation}
\author{Ndagga Nicholas Brenden 15/u/11200/eve}
\date{May, 21, 2017}
\maketitle

\newpage


\subsection{Abstract}
It is common cause that the advent of the mobile telecommunication, particularly the mobile phone has been immensely beneficial to the developing countries like Uganda. Not only has facilitated and improved communication between individuals, but has also enabled economies to grow faster. This paper explores an additional benefit that derives from having access to the mobile phones.it explores the development uses of the mobile phones in Uganda.it examines the relationship between the economic 

\section{Introduction}
	Unlike most other end products, the end product in the mobile telecommunication industry, namely the mobile phone is used extensively  Uganda by people that have access to the mobile phone to upgrade themselves economically  and socially in a remarkably wide variety ways. These  ways range from stating up enterprise in which the mobile phone play a crucial role, to utilizing the mobile phone applications and the platforms constructed by the mobile phone network operators(MNOS).These economic and social upgrading initiatives are mostly developed in nature that they raise the human and productive capacity of the economies in which they are embedded.
	The paper examines the developmental use of mobile phones in Uganda.it commences with the expansion of MTN mobile money services which consist of three types M-transfer-payments and  M-financials services which enable social upgrading to take place-payments also lead to social downgrading


\section{ Significance of the Study}
	The study found a general census among Ugandans for the reason to the use of mobile phones, with the majority of them choosing socialization, safety and privacy. The high emphasis on socializing is in line with the literature which states that the most commonly found reason for owning a mobile phone by most t Ugandans was the convenience of being able to contact others and be contacted regardless of time and location. Robbery and crime are very prevalent in Uganda ,therefore it’s not surprising that most Ugandans regard safety as one of the primary reasons for the use often mobile phones in order to contact someone in case of emergency.it is also associated with privacy in preventing access to discreet information.

\section{Statement of the Problem}
The project focus on the social, economic upgrading relevance of mobile phones in Uganda and the social downgrading results from the use of mobile phones. The evolution of the various telecommunication companies and the various services offered to improve the communication between people.

\section{Chapter 2}
This chapter highlights the findings, diagrams, conclusion and bibliography.
\subsection{Findings }
Today in Uganda mobile money can be loosely be refer to as electronic or virtue money held by individuals electronically.it has demarcated ground –breaking facilities to make financial services more inclusive. Especially for the unbanked population. The mobile money services in Uganda are largely partnered by mobile money network operators like MTN, AIRTEL. Commercial banks act as guarantors for money in Uganda. Although the modes differ slightly the both offer the same services. . The high emphasis on socializing is in line with the literature which states that the most commonly found reason for owning a mobile phone by most t Ugandans was the convenience of being able to contact others and be contacted regardless of time and location. Robbery and crime are very prevalent in Uganda ,therefore it’s not surprising that most Ugandans regard safety as one of the primary reasons for the use often mobile phones in order to contact someone in case of emergency.it is also associated with privacy in preventing access to discreet information.

\section{Literature review}
The literature review therefore focuses on the use of mobile phones in Uganda in the different parts of the country and how mobile phone usage is perceived by most Ugandans.it is acknowledge that it is difficult to draw conclusive arguments of mobile phone use as culture, values and belief systems differ around the world play a part in the perception and use of technology.

\section{Methodology}
The study was descriptive in nature, with the use of the survey to gather the data. The research method selected for this study was a survey approach because it allowed for a larger sample to be gathered, as opposed to interviews or other forms of data gathering. The survey was used to obtain the behavior, opinion and attitudes of many Ugandans with regard to their use of the mobile phones.
The elevated societal status of early adopters of the mobile phones has led to the proud display of the of the handsets owners




\subsection{Conclusion}
This study set out to explore the use of mobile phones in uganda as a contribution to a variety of related fields. Media research has largely ignored the phenomennon of the mobile phones whereas it has increasingly led to more access to the web and other services on the internet among the youth.The availability of other mobile features such as bluetooth or an internal camera define the handsets predefined support for a rannge of other application.Mobile phones can be used to both provide moe interactive means of telling the news from various angles but also to enlarge the potential of various readers and viewer.





\end{document}